Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-07-04 WRITEUP/ms.tex
minor fixes to sect 4

In the clump-finding process (in position-position-position space; PPP), we employ a set of different density thresholds defined based on the molecular hydrogen density of \flower at different evolutionary stages ($z=6.0$--7.2).
%
We note that this process is the three-dimensional analog to identifying molecular structures based on the noise levels in position-position-velocity (PPV) maps that observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN. This is commonly done by
identifying clumps based on/after applying S/N-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; e.g., \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a, DonovanMeyer13a}).
%
%We note that, owing to the nature of \obs, such structures are identified in position-position-velocity (PPV) space, whereas in simulations, one has the full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
Existing studies find a good correspondence in the dynamical properties extracted in PPV- versus PPP-space for well-isolated structures (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, Pan15a}, but see \citealt{Ballesteros-Paredes02a} and \citealt{Shetty10a} for a discussion on caveats and limitations).
% large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig. 1 of Beaumount13a). (may be worth putting more thoughts on this after the report is due).

@@

In \Fig{h2density}, we show the distribution of H$_2$ number density $n_{\rm H2}$ for \flower during its accreting phase, including the contribution from the gas within 3.5 kpc from the galaxy center.
%
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of densities where clumps are found based on morphological analysis\footnote{For $n_{\rm H2}\gtrsim1$\,\cc, the fourth Minkowski functional of the H$_{2}$ density field is significantly larger than zero. This implies that the field is made of isolated components. See Fig. 6 in \citet{Pallottini17b}.} \citep{Pallottini17b}.
%
In each evolutionary stage, we identify MCCs by applying density cuts to the {\em H$_2$ density} distribution, i.e., MCCs
are selected at $n_{\rm cut} \leq n_{\rm H2}$. We select 10 equally-spaced cuts in H$_2$ density in log scale: ${(n_{\rm cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 18.96, 31.62]$.
% We also tested variations in $n_{\rm cut}$ range and found no qualitative differences (see \Sec{ncut}).
Note that with these choice we are including MCCs that are not fully molecular ($n = 0.5 n_{\rm H2}$).

>>>>

In the clump-finding process (in position-position-position space; PPP), we employ a set of different density thresholds defined based on the molecular hydrogen density of \flower at different evolutionary stages ($z=6.0$--7.2).
%
We note that this process is the three-dimensional analog to identifying molecular structures based on the noise levels in position-position-velocity (PPV) maps that observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN. This is commonly done by
identifying clumps based on/after applying S/N-clipping, using tools
such as the \ncode{aips} tasks \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; (e.g., \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a, DonovanMeyer13a})).
%
%We note that, owing to the nature of \obs, such structures are identified in position-position-velocity (PPV) space, whereas in simulations, one has the full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
Existing studies find a good correspondence in the dynamical properties extracted in PPV- versus PPP-space for well-isolated structures (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, Pan15a}, but see \citealt{Ballesteros-Paredes02a} and \citealt{Shetty10a} for a discussion on caveats and limitations).
% large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig. 1 of Beaumount13a). (may be worth putting more thoughts on this after the report is due).

@@

In \Fig{h2density}, we show the distribution of H$_2$ number density $n_{\rm H2}$ for \flower during its accreting phase, including the contribution from the gas within 3.5 kpc from the galaxy center.
%
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of densities where clumps are found based on morphological analysis\footnote{For $n_{\rm H2}\gtrsim1$\,\cc, the fourth Minkowski functional of the H$_{2}$ density field is significantly larger than zero. This implies that the field is made of isolated components. See Fig. 6 in \citet{Pallottini17b}.} \citep{Pallottini17b}.
%
In each evolutionary stage, we identify MCCs by applying density cuts to the {\em H$_2$ density} distribution, i.e., MCCs
are selected at $n_{\rm cut} \leq n_{\rm H2}$. We select 10 equally-spaced cuts in H$_2$ density in log scale: ${(n_{\rm cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 18.96, 31.62]$.
% We also tested variations in $n_{\rm cut}$ range and found no qualitative differences (see \Sec{ncut}).
Note that with these choices we are including MCCs that are not fully molecular ($n = 0.5 n_{\rm H2}$).
